### 2014-08-05 paper/paper.tex
Added a new graph but the data for it is not done. Also worked on the future work section

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal, Or feature
normalization. The F-score that is achieved is \textbf{50.72}.

%TODO consider cleaning the text up here

@@

%TODO add references to the feature selection section

@@

\subsubsection{Negation}
\label{sssection:negation}
%TODO
\subsubsection{N-gram Features}
\label{sssection:ngram}
%TODO
\subsubsection{Employing Sentiment Lexicon}
\label{sssection:sentimentlexicon}

Many of the more complex solutions submitted to the SemEval-2013 workshop made
uses of sentiment lexicons that capture a term's polarity. These lexicons, such
as \href{http://sentiwordnet.isti.cnr.it/}{SentiWordNet}, express the positive,
neutral, and negative sentiment of each homonym.

>>>>

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal (words with a
document frequancy > 1), Or feature normalization. The F-score that is achieved
is \textbf{50.72}.

@@

@@

\subsubsection{Negation}
\label{sssection:negation}

One problem with the current implementation is that it lack support for
negation. In it's current form the classifier would likely misunderstand the
sequence ``not perfect'' since `not' is a vaguely negative word and `perfect'
is a very positive word, it would likely be classified as positive when in fact
the sentiment is quite clearly negative. A common approach to this problem is
to add a suffix (such as "\_NEG") to word that appear between a negation word
and a section delimiting punctuation mark (such as `,', `.', `:', `;', `!',
`?'). By separating negated features from their non-negated instances, features
can do a better job of distinguishing classes.

\subsubsection{N-gram Features}
\label{sssection:ngram}

One way that many of the other bag-of-words solutions capture word order is by
creating features consisting of sequences of words called bigrams. Adding
bigram features adds a large number of features which can add complexity to
training. This concept can also be extended to sequences of length n, called
ngrams.

The added complexity associated with ngrams did not deter the National Research
Council of Canada from using ngrams of length 1, 2, 3, and 4 as well as
`non-contiguous' ngrams which are described as `ngrams with one token replaced
by *' \cite{Mohammad2013}.

\subsubsection{Employing Sentiment Lexicon}
\label{sssection:sentimentlexicon}

Most of the more complex solutions submitted to the SemEval-2013 workshop made
uses of sentiment lexicons that capture a term's polarity. These lexicons, such
as \href{http://sentiwordnet.isti.cnr.it/}{SentiWordNet}, express the positive,
neutral, and negative sentiment of each homonym.
